\documentclass[letterpaper,10pt]{resume}
\usepackage{paralist}
\definecolor{ruleendcolor}{rgb}{0.8,0.8,0.8}

\author{Nicklas O. Stockton}
\email{nick.stockton@outlook.com}
\streetaddress{5274 Brasher Ave.}
\citystatezip{Blue Ash, OH, 45242}
\phone{(719)\hspace{1pt}648-3545}


\begin{document}
	\maketitle
	\section{Education}
	\affiliation[Bachelor of Science \textendash\ Aerospace Engineering, Dean's List]
	[Cincinnati, OH]
	{University of Cincinnati}
	{2013\textendash Present}
	
	\begin{itemize}
		\item GPA: 3.87 overall, 3.90 in Aerospace Engineering
		\item Expected graduation: Spring 2017
	\end{itemize}

	\section{Research \& Extracurricular}
	\affiliation[Autonomous Air Vehicle Competition Team Member]
	{Air Force Research Labs Autonomous Air Vehicle Conference}
	{2014\textendash Present}
	\begin{itemize}
		\item Competition challenge requirements included locating and imaging a target in an indoor,\\ GPS\textendash denied environment.
		\item Developed software to integrate various hardware components to ease the exchange of sensor\\ data.
		\item Software processes raw data streams from serial connections to useful information to be used\\ in the control and guidance of the air vehicle.
		\item Current work includes developing improved computer vision algorithms and interpreting\\ encoded waypoint information.
	\end{itemize}
	
	\affiliation[Undergraduate Research]
	{National Science Foundation}
	{2013}
	\begin{itemize}
		\item Analyzed a benchmark structural stability problem to devise a control methodology\\  using fuzzy\textendash genetic systems.
		\item System model exhibited both flexible and rigid body modes. Designed controller performed\\ within 3\% of theoretically ascertained limit of stability.
		\item Controller consists of a genetically\textendash tuned fuzzy inference system.
		\item Presented findings before a peer audience at multiple conferences.
	\end{itemize}	
	\pagebreak
	
	\section{Professional Experience}
	\affiliation[Research Engineer]
	[Cincinnati, OH]
	{Engineering and Scientific Innovations, Inc.}
	{2014\textendash Present}
	\begin{compactitem}
		\item Overhauled proprietary fire suppressant delivery system resulting in a 70\% efficiency gain.
		\item Assisted in the prototyping and proof of concept for flow introduction of powdered agent. 
		\item Performed high\textendash speed cavity analysis of hydrodynamic ram events using custom computer code.
	\end{compactitem}
	
	\affiliation[Sole Owner and Operator]
	[Colorado Springs, CO/ Provo, UT]
	{Green It Up LLC\textemdash Lawn Care Company}
	{2011\textendash 2013}
	\begin{compactitem}
		\item Grossed \$24,000 in sales in first year of operation.
		\item Satisfied needs of  more than 100 regular clients.
		\item Maintained brand equity through personal management of 3 employees.
		\item Managed own finances, accounting and bookkeeping.
		\item Bought out business partner 3 months after start-up.
		\item Successfully facilitated transition of business from Colorado to Utah.
	\end{compactitem}
	
	\affiliation[Volunteer Representative, LDS Church]
	[Philippines]
	{Philippines Bacolod/Iloilo Mission}
	{2008\textendash 2010}
	\begin{compactitem}
		\item Learned instructional material in foreign language in 4 months.
		\item Designed and delivered weekly training sessions for up to 20 volunteers.
		\item Conducted weekly goal setting and accountability meetings.
	\end{compactitem}
	
	\affiliation[Crew Leader]
	[Colorado Springs, CO]
	{Intermountain Lawns}
	{2007\textendash 2008}
	\begin{compactitem}
		\item Led and supervised crew of 2\textendash 3 people daily.
		\item Handled and resolved on-site customer concerns.
		\item Improved maintenance procedure for all company equipment.
		\item Streamlined daily operations, improving efficiency of small team.
	\end{compactitem}
	
	\affiliation[Flight Line Assistant]
	[USAF Academy, CO]
	{Embry\textendash Riddle Aeronautical University}
	{2005\textendash 2006}
	\begin{compactitem}
		\item Scheduled flight for over 100 students daily.
		\item Cleaned and maintained aircraft to ensure flight safety.
		\item Streamlined student check\textendash in process, increasing instructional flight time.
	\end{compactitem}


	\section{Skills}
	\begin{compactitem}
	\item Beginner to intermediate proficiency in Autodesk AutoCAD and Inventor Pro.
	\item Basic software development using \textsc{Matlab}, Python and Visual Basic for Applications.
	\item \LaTeX\ document preparation and typesetting.
	\item Familiarity with Linux-based operating systems (Debian derivatives).
	\end{compactitem}
	
	\section{Publications}
	\begin{compactitem}
		\item Janson, A., Stockton, N., Cohen, K., ``Genetic Optimization of Fuzzy Logic Control for Coupled Dynamic Systems'', \emph{SciTech}, AIAA, Kissimmee, FL, 2015.
		\item Brown, B., Crowell, C., Feie, B., Hartmann, J., Hutchins, B., Kukreti, S., Mummidivarapu, S., Redmond, B., Sathyan, A., Stockton, N., Stubblebine, A., Kivelevitch, E., Cohen, K., ``Development and Validation for the First Annual AAVC Competition by the University of Cincinnati Autonomous Vehicle Group'', \emph{Autonomous Aerial Vehicle Conference}, AFRL, Wright\textendash Patterson Air Force Base, OH, 2014.
	\end{compactitem}
\end{document}